Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM

### 2018-08-14 doc/issre2018/framework.tex
Prepared camera ready

Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}. As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with its type signature. Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic generation, logging and so on. Experimentally, we have found an optimal configuration that we consistently used in the experimental evaluation in Section~\ref{sec.evaluation}. Once all data have been processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), an instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}). Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client. Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order. For each branch, our framework enters the \emph{Genetic Loop (Phase)}. Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criterion is achieved, e.g. the limit on the number of generation attempts. Any HTML document produced during the genetic phase should be approved by the \Validator. Each candidate in the population is evaluated in \emph{Evaluation Loop} by \Client. First, the candidate solution $p$ is matched with the type signature \emph{sig}. Then, the instrumented function \emph{ifun} is called (\emph{ifun(p)}). The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed. A new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}. At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User. Once all the branches are covered, the algorithm terminates. Below, we elaborate on the details of each individual phase of our test generation framework.

@@

During the \emph{Initialization Phase} we analyze the FUT in order to facilitate the subsequent genetic testing. The main steps of this phase are described in Algorithm~\ref{alg.init}. Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}. In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants such as numeric and string literals. Additionally, we monitor the calls to the functions \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName} and other DOM API methods. They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the body of the FUT. The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g. transform \emph{if-then} branches into \emph{if-then-else}. We instrument the FUT (line~\ref{alg.init.instr}) in order to collect at run-time the values of the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants. Upon the \emph{ifun} execution this information will be gathered and fed back to the fitness evaluation procedure. Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and return all branches of the FUT (line~\ref{alg.init.get.branches}).

@@

<Signature> ::= \texttt{dom} : <Type Signature> | <Type Signature>

@@

<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}

@@

We assume the FUT is equipped with its type signature. The legitimacy of such requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference, e.g. \emph{Flow}~\cite{flow}. The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}. Each type annotation is a signature expressed as a specialized JS type comment (\texttt{/*t...*/}). We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures. The former kind expects the \texttt{dom} terminal to be in place of the first parameter of the function call. Whereas an ordinary JS signature is a non-empty sequence of the JS types. The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).

%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
%%        LEFT OUT DUE TO LACK OF SPACE
%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\subsubsection{Instrumentation}
\label{sub.sec.instrument}

Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation. The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT. We have to trace all the statements because each one, in theory, can rise an exception. The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations. If the exact bound is unknown, it is set to one. The \texttt{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.

@@

\begin{figure}[!t]
  \tiny
  \begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\tiny\ttfamily}]
function isGameFinished() {
 trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
 trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
 var allOk = true;
 loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
   var no = 0;
   if (subDivs.length || subDivs.length == 0) {
     return Math.abs(no - subDivs.length);
   }; return 1}();
 trace.push(3);
 for (var no = 0; no < subDivs.length; no++) {
  trace.push(4);
  if (subDivs[no].className.indexOf("square") >= 0 &&
      !subDivs[no].style.backgroundColor) {
   trace.push(5); branchDistance.push({ label: 3,
    distance: Math.min(
     abs(subDivs[no].className.indexOf("square"),0)+_K_
     absZero(subDivs[no].style.backgroundColor))
   });
   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
   trace.push(7);
   if (spans[0].innerHTML != spans[1].innerHTML) {
    trace.push(8); branchDistance.push({ label: 7,
     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
    });
    allOk = false; break;
   } else {
   trace.push(9);branchDistance.push({label:7,distance:_K_});
   }
  } else {
   trace.push(10); branchDistance.push({ label: 3,
    distance:
     abs(subDivs[no].className.indexOf("square"), 0) +
     absNegZero(subDivs[no].style.backgroundColor)
   });}}
 trace.push(-1); return allOK;
}
\end{lstlisting}
  \caption{Instrumented version of \texttt{isGameFinished.js} }
  \label{code.isGameFinished.instr}
\end{figure}

@@

At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$. If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target. It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}). Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$. In practice, we only consider extensions upto length two.

@@

\begin{table}[!t]
  \caption{Genetic Operation for the JS Types}
  \label{tbl.gen.oper.js.types}
  \scriptsize
  \centering
  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
    \toprule
    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
    \hline
    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
    Random    & Int    & choose (4:1) at random [-10, 10] or constants\\
    Random    & Float  & choose (4:1) at random [-10.0, 10.0] or constants\\
    Random    & String & $>5$ chars from $\texttt{[a-zA-Z0-9]}$ or constants (4:1)\\
    Random    & Array  & array of a respective type upto length five\\
    \hline
    Crossover & Bool   & pick at random one out of two given booleans \\
    Crossover & Int    & pick at random one out of two given integers\\
    Crossover & Float  & pick at random one out of two given floats\\
    Crossover & String & pick at random one out of two single point crossovers\\
    Crossover & Array  & similar crossover operator as for strings\\
    \hline
    Mutation  & Bool   & flip the boolean constant\\
    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
    Mutation  & String & random string, remove char or apply pred(suc) char\\
    Mutation  & Array  & Mutate a random element in array according to its type\\
    \bottomrule
  \end{tabular}
\end{table}

@@

data Tag = HTML | HEAD | BODY | ...
type Context = CFlow | CMetadata | ...
data HtmlState = |c \label{ref.HtmlState.begin} |c
  HtmlState { depth    :: Int,           degree  :: Int
             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)]
             , tags    :: [Tag],         ids     :: [String]
             , classes :: [String] } |c \label{ref.HtmlState.end} |c
type GenState s = StateT s Gen |c \label{ref.GenState} |c
type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
  \end{haskell}
  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
  \label{fig.html.arb.def}
\end{figure}

@@

In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML. This was a challenge on its own because the complexity of HTML and the lack of formal specification. Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type. With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition. The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}. The state is composed of the following components:
\begin{itemize}
\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML
\item \texttt{ctx} is the current value of the HTML content model stack
\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
\end{itemize}
Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}). Each HTML tag is the value of the \texttt{GenHtmlState} type. Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag. According to the specification~\cite{htmlspec}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag. First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively). Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}). Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their composition (line~\ref{ref.generateHTML.end}).

@@

In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels. Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.

\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.

>>>>

Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}. As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with its type signature. Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic generation, logging and so on. Experimentally, we have found an optimal configuration that we consistently used in the experimental evaluation in Section~\ref{sec.evaluation}. Once all data have been processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), an instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}). Then, the \Server sends a \jsID{POST} request with \emph{ifun} and \emph{sig} to the \Client. Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order. For each branch, our framework enters the \emph{Genetic Loop (Phase)}. Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criterion is achieved, e.g. the limit on the number of generation attempts. Any HTML document produced during the genetic phase should be approved by the \Validator. Each candidate in the population is evaluated in \emph{Evaluation Loop} by \Client. First, the candidate solution $p$ is matched with the type signature \emph{sig}. Then, the instrumented function \emph{ifun} is called (\emph{ifun(p)}). The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed. A new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}. At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User. Once all the branches are covered, the algorithm terminates. Below, we elaborate on the details of each individual phase of our test generation framework.

@@

During the \emph{Initialization Phase} we analyze the FUT in order to facilitate the subsequent genetic testing. The main steps of this phase are described in Algorithm~\ref{alg.init}. Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}. In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants such as numeric and string literals. Additionally, we monitor the calls to the functions \jsID{getElementsByTagName}, \jsID{getElementById}, and \jsID{getElementsByClassName} and other DOM API methods. They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the body of the FUT. The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g. transform \emph{if-then} branches into \emph{if-then-else}. We instrument the FUT (line~\ref{alg.init.instr}) in order to collect at run-time the values of the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants. Upon the \emph{ifun} execution this information will be gathered and fed back to the fitness evaluation procedure. Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and return all branches of the FUT (line~\ref{alg.init.get.branches}).

@@

<Signature> ::= \jsID{dom} : <Type Signature> | <Type Signature>

@@

<Primitive Type> ::= \jsID{bool} | \jsID{int} | \jsID{float} | \jsID{string}

@@

We assume the FUT is equipped with its type signature. The legitimacy of such requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference, e.g. \emph{Flow}~\cite{flow}. The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}. Each type annotation is a signature expressed as a specialized JS type comment (\jsID{/*t...*/}). We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures. The former kind expects the \jsID{dom} terminal to be in place of the first parameter of the function call. Whereas an ordinary JS signature is a non-empty sequence of the JS types. The type can be \emph{Void}, \emph{Primitive} (\jsID{bool}, \jsID{int}, \jsID{float}, \jsID{string}) or \emph{Array} (recursive homogeneous array type).

\subsubsection{Instrumentation}
\label{sub.sec.instrument}

The instrumented version of the FUT is shown in Figure~\ref{code.isGameFinished.instr}. The global variable \jsID{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT. We have to trace all the statements because each one, in theory, can rise an exception. The \jsID{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations. If the exact bound is unknown, it is set to one. The \jsID{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.

@@

\begin{figure}[!t]
  \tiny
  \begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\tiny\ttfamily}]
function isGameFinished() {
 trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
 trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
 var allOk = true;
 loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
   var no = 0;
   if (subDivs.length || subDivs.length == 0) {
     return Math.abs(no - subDivs.length);
   }; return 1}();
 trace.push(3);
 for (var no = 0; no < subDivs.length; no++) {
  trace.push(4);
  if (subDivs[no].className.indexOf("square") >= 0 &&
      !subDivs[no].style.backgroundColor) {
   trace.push(5); branchDistance.push({ label: 3,
    distance: Math.min(
     abs(subDivs[no].className.indexOf("square"),0)+_K_
     absZero(subDivs[no].style.backgroundColor))
   });
   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
   trace.push(7);
   if (spans[0].innerHTML != spans[1].innerHTML) {
    trace.push(8); branchDistance.push({ label: 7,
     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
    });
    allOk = false; break;
   } else {
   trace.push(9);branchDistance.push({label:7,distance:_K_});
   }
  } else {
   trace.push(10); branchDistance.push({ label: 3,
    distance:
     abs(subDivs[no].className.indexOf("square"), 0) +
     absNegZero(subDivs[no].style.backgroundColor)
   });}}
 trace.push(-1); return allOK;
}
\end{lstlisting}
  \caption{Instrumented version of \jsID{isGameFinished.js} }
  \label{code.isGameFinished.instr}
\end{figure}

@@

At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$. If it has converged (line~\ref{alg.gen.loop.end}), the GA is restarted with a new search target, which is composed of the original branch $b_n$ prefixed with a branch $b$ on which $b_n$ depends (line~\ref{alg.gen.new.target}). This process is exhaustively repeated to test all possible executions leading to $b_n$. In practice, we only consider extensions upto length two.

@@

\begin{table}[!t]
  \caption{Genetic Operation for the JS Types}
  \label{tbl.gen.oper.js.types}
  \scriptsize
  \centering
  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
    \toprule
    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
    \hline
    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
    Random    & Int    & choose (4:1) at random [-10, 10] or constants\\
    Random    & Float  & choose (4:1) at random [-10.0, 10.0] or constants\\
    Random    & String & $>5$ chars from $\jsID{[a-zA-Z0-9]}$ or constants (4:1)\\
    Random    & Array  & array of a respective type upto length five\\
    \hline
    Crossover & Bool   & pick at random one out of two given booleans \\
    Crossover & Int    & pick at random one out of two given integers\\
    Crossover & Float  & pick at random one out of two given floats\\
    Crossover & String & pick at random one out of two single point crossovers\\
    Crossover & Array  & similar crossover operator as for strings\\
    \hline
    Mutation  & Bool   & flip the boolean constant\\
    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
    Mutation  & String & random string, remove char or apply pred(suc) char\\
    Mutation  & Array  & Mutate a random element in array according to its type\\
    \bottomrule
  \end{tabular}
\end{table}

@@

data Tag = HTML | HEAD | BODY | ...
type Context = CFlow | CMetadata | ...
data HtmlState = |c \label{ref.HtmlState.begin} |c
  HtmlState { depth    :: Int,           degree  :: Int
             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)]
             , tags    :: [Tag],         ids     :: [String]
             , classes :: [String] } |c \label{ref.HtmlState.end} |c
type GenState s = StateT s Gen |c \label{ref.GenState} |c
type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
  \end{haskell}
  \caption{The \jsID{Arbitrary} instance for the \jsID{Html} data type}
  \label{fig.html.arb.def}
\end{figure}

@@

In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML. This was a challenge on its own because the complexity of HTML and the lack of formal specification. Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \jsID{Arbitrary} instance for the \jsID{Html} data type. With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition. The data type \jsID{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \jsID{Html}. The state is composed of the following components:
\begin{itemize}
\item \jsID{depth} and \jsID{degree} specify respectively the maximum depth and node degree of the generated HTML
\item \jsID{ctx} is the stack of HTML contexts
\item \jsID{tagFreq} provides statistical information about the frequency of tags in HTML
\item \jsID{tags}, \jsID{ids} and \jsID{classes} are the initial set of respective HTML elements used for random generation.
\end{itemize}
Combined with the random generation monad \jsID{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \jsID{Html} (line~\ref{ref.GenHtmlState}). Each HTML tag is the value of the \jsID{GenHtmlState} type. Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \jsID{<html>} tag. According to the specification~\cite{htmlspec}, the tag is composed of the \jsID{<head>} tag followed by the \jsID{<body>} tag. First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively). Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}). Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \jsID{head} (line~\ref{ref.generateHTML.newHead}) and \jsID{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their composition (line~\ref{ref.generateHTML.end}).

@@

In essence, an HTML document is a labeled tree, where nodes are \emph{tags} and labels are \emph{attributes}. So, crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.

\textbf{HTML Crossover} takes two documents, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.

### 2018-08-14 doc/issre2018/introduction.tex
Prepared camera ready

According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language. It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million). The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}. On the other hand, due to implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}. Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc~\cite{bugstories2017}.

Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}. There exist numerous JS frameworks on the market --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc. --- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests. Despite the apparent abundance of the JS testing tools, developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements. One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}. It pursues the goal of maximizing test coverage by exercising the function under test (FUT) with various input parameters. Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.

The problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach. In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. We summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}

>>>>

According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript (JS) has been recognized for the sixth time in row as the most commonly used programming language. It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million). The success of JS can be explained by its native browsers support, and the rise in popularity of the JS runtime environment \emph{Node.js}. On the other hand, JS applications are error-prone~\cite{frolin:TSE16} and challenging to test and analyze~\cite{mesbah2015advances,andreasen2017survey,sun2017analysis} due to such language features as implicit type conversion, lack of static types, and extensive support of dynamic constructs~\cite{richards2010analysis}. Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc.~\cite{bugstories2017}.

Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}. There exist numerous JS frameworks on the market
--- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc. ---
intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests. Despite the apparent abundance of the JS testing tools, developers satisfaction  is still relatively low~\cite{stateJS2017} (3.2 out of 5), indicating there is a room for improvements. One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}. It pursues the goal of maximizing test coverage by exercising the function under test (FUT) with various input parameters. Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.

The problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\mbox{\emph{JSContest}}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach. In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. We summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (including \emph{tags} and \emph{attributes}), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}
